Paper Visualization

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
made changes

# Load Directories
output_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage"
threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads"
comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments"

@@

@@

# Remove sparse terms to reduce the size of DTM
dtm <- removeSparseTerms(dtm, 0.92) # Adjust sparsity threshold if necessary

@@

```{Top Terms}
# Display the top terms for each topic
top_terms <- terms(lda_model, 10)
print(top_terms)

# Visualize the top terms for each topic (concise visualization)
top_terms_df <- tidy(lda_model, matrix = "beta") %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

@@

```{r Co-occurrence Network Analysis}
# Create a co-occurrence matrix
term_matrix <- as.matrix(dtm)
co_occurrence <- crossprod(term_matrix)

# Build graph object
graph <- graph_from_adjacency_matrix(co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)
V(graph)$name <- colnames(co_occurrence)

# Simplify graph (remove loops and multiple edges)
graph <- simplify(graph)

# Visualize co-occurrence network
set.seed(123)
ggraph(graph, layout = 'fr') + 
  geom_edge_link(aes(edge_alpha = weight), show.legend = FALSE) + 
  geom_node_point(color = "blue", size = 5) + 
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void() +
  labs(title = "Co-occurrence Network of Themes")
```

>>>>

# Load Directories
output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage"
threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads"
comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments"

@@

```{r Filtering For Relevancy}
# Load necessary libraries
library(ggplot2)
library(dplyr)

# Calculate the minimum and maximum of the 'Thread_Relevancy' column
min_value <- min(all_threads$Thread_Relevancy, na.rm = TRUE)
max_value <- max(all_threads$Thread_Relevancy, na.rm = TRUE)

# Create four equal-sized bins between the min and max values
breaks <- seq(min_value, max_value, length.out = 5)

# Create a factor for quartile ranges based on these breaks
all_threads$Quartile <- cut(
  all_threads$Thread_Relevancy,
  breaks = breaks,
  labels = c("Q1", "Q2", "Q3", "Q4"),
  include.lowest = TRUE
)

# Plot the bar graph showing the frequency of each quartile
ggplot(all_threads, aes(x = Quartile)) +
  geom_bar(fill = "skyblue", color = "black") +
  geom_text(stat='count', aes(label=..count..), vjust=-0.5) +  # Add labels above bars
  labs(title = "Frequency of Thread Relevancy Quartiles",
       x = "Quartile",
       y = "Frequency") +
  theme_minimal()

# Define the bin width manually
bin_width <- 0.5

# Plot the histogram with density overlay using all_threads
ggplot(all_threads, aes(x = Thread_Relevancy)) +
  geom_histogram(aes(y = ..count..), binwidth = bin_width, fill = "skyblue", color = "black", alpha = 0.7) + 
  geom_density(aes(y = ..density.. * length(all_threads$Thread_Relevancy) * bin_width), fill = "orange", alpha = 0.4) +  # Scale density to match histogram counts
  labs(title = "Histogram and Density of Thread Relevancy Scores",
       x = "Relevancy",
       y = "Number of Threads") +
  theme_minimal()
```

```{r}
# Filter out Quartile 1
filtered_threads <- all_threads %>%
  filter(Quartile != "Q1")

# Plot the bar graph showing the frequency of each quartile
ggplot(filtered_threads, aes(x = Quartile)) +
  geom_bar(fill = "skyblue", color = "black") +
  geom_text(stat='count', aes(label=..count..), vjust=-0.5) +  # Add labels above bars
  labs(title = "Frequency of Thread Relevancy Quartiles",
       x = "Quartile",
       y = "Frequency") +
  theme_minimal()

# Define the bin width manually
bin_width <- 0.5

# Plot the histogram with density overlay using all_threads
ggplot(filtered_threads, aes(x = Thread_Relevancy)) +
  geom_histogram(aes(y = ..count..), binwidth = bin_width, fill = "skyblue", color = "black", alpha = 0.7) + 
  geom_density(aes(y = ..density.. * bin_width * nrow(all_threads)), fill = "orange", alpha = 0.4) +  # Scale density to match histogram counts
  labs(title = "Histogram and Density of Thread Relevancy Scores",
       x = "Relevancy",
       y = "Number of Threads") +
  theme_minimal()
```
```{r Get Filtered Comments from Filtered Threads}
# Filter threads with only one comment out of filtered threads 
filtered_threads <- filtered_threads %>%
  filter(Number.of.Messages > 1)

# Filter the comments from 'all_comments' that match the filtered threads
filtered_comments <- all_comments %>%
  filter(Thread.ID %in% filtered_threads$Unique_ThreadID)

# Check the result
head(filtered_comments)
```

```{r Relevancy Filtered Descriptive Statistics}
library(sjPlot)

# Step 1: Group by newsgroup and calculate required statistics, including comment relevancy
keywords_summary_df <- filtered_comments %>%
  group_by(newsgroup) %>%
  summarize(
    Unique_Authors = n_distinct(Author),
    Comments_with_Keywords = sum(Relevancy > 0),
    Conversations_Mentioned_In = n_distinct(Thread.ID),
    Total_Comments_In_Threads = n(),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
    Average_Relevancy_Score = mean(Relevancy, na.rm = TRUE)
  )

# Step 2: Calculate thread relevancy averages for filtered threads
threads_summary_df_grouped <- filtered_threads %>%
  group_by(newsgroup) %>%
  summarize(Average_Thread_Relevancy = mean(Thread_Relevancy, na.rm = TRUE))

# Step 3: Combine comment and thread summaries
keywords_summary_df <- keywords_summary_df %>%
  left_join(threads_summary_df_grouped, by = "newsgroup")

total_unique_authors <- n_distinct(filtered_comments$Author)

# Step 4: Add a totals row
totals <- keywords_summary_df %>%
  summarize(
    newsgroup = "Total",
    Comments_with_Keywords = sum(Comments_with_Keywords),
    Conversations_Mentioned_In = sum(Conversations_Mentioned_In),
    Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
    Unique_Authors = total_unique_authors,
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
    Average_Relevancy_Score = mean(Average_Relevancy_Score, na.rm = TRUE),
    Average_Thread_Relevancy = mean(Average_Thread_Relevancy, na.rm = TRUE)
  )

# Step 5: Combine the summary with the totals row
keywords_summary_df <- bind_rows(keywords_summary_df, totals)

# Correctly construct the output file path
output_file_path <- file.path(output_directory, "images and tables", "aids_descriptive_statistics_table_relevancy_filtered.html")

# Ensure the directory exists
dir.create(dirname(output_file_path), recursive = TRUE, showWarnings = FALSE)

# Use the constructed path for saving the file
tab_df(keywords_summary_df, file = output_file_path)
```

@@

# Remove sparse terms to reduce the size of DTM
dtm <- removeSparseTerms(dtm, 0.90) # Adjust sparsity threshold if necessary

@@

```{r Top Terms}
# Display the top terms for each topic
top_terms <- terms(lda_model, 20)
print(top_terms)

# Visualize the top terms for each topic (concise visualization)
top_terms_df <- tidy(lda_model, matrix = "beta") %>%
  group_by(topic) %>%
  top_n(20, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

@@

```{r Co-occurrence Network Analysis}
# Step 1: Filter out terms with lower frequencies or less importance
# You may set a threshold for filtering less relevant terms
term_frequency <- rowSums(co_occurrence) # Calculate term frequency
threshold <- quantile(term_frequency, 0.9) # Set threshold for top 10% most frequent terms
filtered_terms <- which(term_frequency > threshold)
filtered_co_occurrence <- co_occurrence[filtered_terms, filtered_terms]

# Step 2: Create graph object with filtered terms
graph <- graph_from_adjacency_matrix(filtered_co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)

# Step 3: Simplify the graph to avoid self-loops and redundant edges
graph <- simplify(graph)

# Step 4: Visualize the co-occurrence network with improved settings
set.seed(123)  # For reproducibility
ggraph(graph, layout = 'fr') + 
  geom_edge_link(aes(edge_alpha = weight), show.legend = FALSE, edge_width = 0.2) + 
  geom_node_point(color = "blue", size = 4) + 
  geom_node_text(aes(label = name), repel = TRUE, max.overlaps = 20) + # Increase max.overlaps for ggrepel
  theme_void() +
  labs(title = "Co-occurrence Network of Key Themes")
```
